Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-12-05 referee_2.tex
Fixing typo in response v2

    The convergence study is a great addition to the paper. However, the lowest limit explored here (0.625pc) is a factor of roughly 100 larger than the scale on which fragmentation can be seen (compare eg the 1000AU regions, in which several Pop III stars form in work by Stacy+16). I recommend to explicitly state down to which resolution the convergence was tested in Section 2.2.1 and adding these limitations to the "Caveats" section. Instead of single Pop III stars, this paper is a study of the multiplicity of Pop III star formation regions. Please make this clear in the paper. 
\end{referee}
    In Section 2.2, we have expanded our description of the convergence study to include the smallest resolution and pointed out that the overdensity formation criterion is similar to a molecular core.  We explicitly state that our results are lower limits on the number of Pop III stars, massive and low-mass, in this section.  Furthermore, we remind the reader about this lower limit in Section 3.3, where we present our results on the stellar multiplicity.  Lastly, we have added a paragraph in the Caveats section (S4.3) about our simulation not resolving fragmentation below 0.625 pc and conclude that our work strengthens the case for multiple Pop III stars in each halo, especially considering this limitation.

@@

\begin{referee}
    - The authors put their work in comparison to Schauer+19, ApJL 877, 5 who match the star formation efficiency in minihaloes to the observed 21cm signal. They should rather compare to Schauer+19 MNRAS, 484, 3510 who performed cosmological hydrodynamical simulations for the minimum and average halo mass in different streaming velocity regions. Please include their limits in your Figure 10, as done with the Naoz+13 results, and a short comparison to Hirano+18 (their Science paper). Please include these references also in the introduction. Also the sentence "Often in the literature, streaming velocities are only studied for a few haloes" seems outdated.
\end{referee}
    We have added a panel to the left of Figure 10 to de-clutter the main figure and to separate the halo mass ranges and minimums related to streaming velocities.

@@

    We have added a short comparison to Hirano+17 (Science) and have also added their citation to the list of citations mentioned previously.

>>>>

    The convergence study is a great addition to the paper. However, the lowest limit explored here (0.625pc) is a factor of roughly 100 larger than the scale on which fragmentation can be seen (compare eg the 1000AU regions, in which several Pop III stars form in work by Stacy+16). I recommend to explicitly state down to which resolution the convergence was tested in Section 2.2.1 and adding these limitations to the "Caveats" section. Instead of single Pop III stars, this paper is a study of the multiplicity of Pop III star formation regions. Please make this clear in the paper. 
\end{referee}
    In Section 2.2, we have expanded our description of the convergence study to include the smallest resolution and pointed out that the overdensity formation criterion is similar to a molecular core.  We explicitly state that our results are lower limits on the number of Pop III stars, massive and low-mass, in this section.  Furthermore, we remind the reader about this lower limit in Section 3.3, where we present our results on the stellar multiplicity.  Lastly, we have added a paragraph in the Caveats section (\S4.3) about our simulation not resolving fragmentation below 0.625 pc and conclude that our work strengthens the case for multiple Pop III stars in each halo, especially considering this limitation.

@@

\begin{referee}
    - The authors put their work in comparison to Schauer+19, ApJL 877, 5 who match the star formation efficiency in minihaloes to the observed 21cm signal. They should rather compare to Schauer+19 MNRAS, 484, 3510 who performed cosmological hydrodynamical simulations for the minimum and average halo mass in different streaming velocity regions. Please include their limits in your Figure 10, as done with the Naoz+13 results, and a short comparison to Hirano+18 (their Science paper). Please include these references also in the introduction. Also the sentence "Often in the literature, streaming velocities are only studied for a few haloes" seems outdated.
\end{referee}
    We have added a panel to the left of Figure 10 to de-clutter the main figure and to separate the halo mass ranges and minima related to streaming velocities.

@@

    We have added a short comparison to Hirano+17 (Science) and Schauer+19 have also added their citation to the list of citations mentioned previously.
